Predicting Success of Motivational Interviews with Recurrent Neural Network and Probabilistic Model for Patient-Provider Communication Sequences

### 2017-09-12 paper-amia-summit-2018/amia_summit_2018.tex
update embedding section

\textbf {Embedding}: We are inspired by the idea of word embedding to represent behavior code of the sequences. Word embedding is a representation of words in low-dimensional space by vectors which contain the feature of the words. In our study, we employed embedding in place of one-hot vectors for the representation of behavior code. Because one-hot vectors are high-dimensional and sparse. On the other hand, code embeddings have the ability to represent semantically similar codes with similar vectors in a low-dimensional space by retaining their internal relations. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding in 44-dimensional vector space visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that positive behavior codes such as OQECHT+, OQECML+, AF, ADV+, RCML+S, CQECML+, etc. formed a cluster which is highlighted in the left part of the figure. However, right part of the figure illustrates another cluster formed with negative behaviors including CQECML-, RCHT-C, OQECHT-, GINFO-, RBAC, LUP-, RCHT-S, RPTBC, RAMBC, AMB-, RCML-S, etc. Because they are semantically similar in the low dimensional vector space.

>>>>

\textbf {Embedding}: We are inspired by the idea of word embedding \cite{bengio2003neural} to represent behavior code of the sequences. Word embedding is a representation of words in low-dimensional space by vectors which contain the feature of the words. In our study, we employed embedding in place of one-hot vectors for the representation of behavior code. Because one-hot vectors are high-dimensional and sparse. On the other hand, code embeddings have the ability to represent semantically similar codes with similar vectors in a low-dimensional space by retaining their internal relations. Figure~\ref{fig:code_embedding} illustrates the myscope code embedding in 44-dimensional vector space visualize with t-SNE, a sophisticated technique for visualizing high-dimensional data. It can be seen that positive behavior codes such as OQECHT+, OQECML+, AF, ADV+, RCML+S, CQECML+, etc. formed a cluster which is highlighted in the left part of the figure. However, right part of the figure demonstrates another cluster formed with negative behavior codes including CQECML-, RCHT-C, OQECHT-, GINFO-, RBAC, LUP-, RCHT-S, RPTBC, RAMBC, AMB-, RCML-S, etc. Because they are semantically similar in the low dimensional vector space.
